Suppl. Figure 2. Differential bacterial abundance across Tissue and Luminal microbiome

### 2022-01-31 reports/rmarkdown/manuscript/Suppl.Figure2.Rmd
changes to accomoadate Paulos new niceRplot code

---
title: "Suppl. Figure 2. Differential bacterial abundance across tissue and CVL microbiome"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

@@

write.xlsx(res, file=paste0("../../../results/","DBA_across_Luminal_vs_Tissue",".xlsx"))

ord <- factor(sapply(unique(as.character(res$bacteria)),function(x){getcluster(all_microbiome, x, datasets)}))

figlabels <- letters
par(mfrow=c(1,2),mar=c(2,12,1,3.1))
#par(mar=c(2,17,1,2)) #b,l,t,r
plot_dots( all_microbiome , names(sort(ord)) , clustering = datasets,
           show_grid = T,cex.main=1,font.main=1,
           cex.row = .8,cex.col = .8,srt = 0)
add_letter("a")
barlist( all_microbiome , names(sort(ord)) , clustering = datasets,
         show_grid = T,cex.main=1,font.main=1,
         cex.axis = .8,srt = 0)
add_letter("b")
```

>>>>

---
title: "Suppl. Figure 2. Differential bacterial abundance across Tissue and Luminal microbiome"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

@@

#write.xlsx(res, file=paste0("../../../results/","DBA_across_Luminal_vs_Tissue",".xlsx"))

ord <- getcluster(data = all_microbiome, genes =  unique(as.character(res$bacteria)), clustering =  datasets)
ord <- ord[unique(as.character(res$bacteria))]

figlabels <- letters
par(mfrow=c(1,2),mar=c(2,12,1,3.1))
plot_dots( all_microbiome, genes = names(sort(ord)) , clustering = datasets,
           show_grid = T,cex.main=1,font.main=1,
           cex.row = .8,cex.col = .8,srt = 0)
add_letter("a")
barlist( all_microbiome, names(sort(ord)) , clustering = datasets,
         show_grid = T,cex.main=1,font.main=1,
         cex.axis = .8,srt = 0)
add_letter("b")

dev.off()
```
